\documentclass[hidelinks]{resume}

\usepackage[left=0.5in,top=0.6in,right=0.5in,bottom=0.6in]{geometry}
\usepackage{mathpazo}
\usepackage{hyperref}
\urlstyle{same}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{multicol}
\setlength{\multicolsep}{3pt}
\setlength{\columnsep}{20pt}

\name{Evan Goode}
\address{\href{mailto:mail@evangoo.de}{mail@evangoo.de} \\ \href{tel:+1-404-917-3321}{+1 (404) 917 3321} \\ Atlanta, GA}
\address{\url{https://github.com/evan-goode}}
\begin{document}

\begin{rSection}{Selected Skills \& Interests}
	\begin{itemize}[nosep,noitemsep,leftmargin=*]
		\renewcommand{\labelitemi}{\tiny$\blacksquare$}
		\begin{multicols}{2}[]
			\item Full-stack web development with HTML, CSS, JS, TypeScript, React, Node.js, Go
			\item Linux systems programming with Rust, Zig, C
			\item Other software development in Python, Go, Node.js
			\item GNU/Linux systems administration, Nix/NixOS
			\item Virtualization and containerization technologies such as libvirt/KVM/QEMU, Docker
			\columnbreak
			\item High-level systems design and problem solving
			% \item Agile software development via Kanban or Scrum
			\item Working with geographically-distributed teams
			\item Free/Libre open-source software development, Git
			\item Documentation, technical writing, writing highly-maintanable code
			\item Cryptography, secure systems, reverse engineering
		\end{multicols}
	\end{itemize}
\end{rSection}

\begin{rSection}{Education}
	\begin{rSubsection}{M.S. Computer Science}{Expected Fall 2022}{Georgia Institute of Technology}{}
	Specialization in Computing Systems. GPA: 4.00 \\
	Selected coursework: Advanced Topics in Malware Analysis, High
Performance Parallel Computing, Applied Cryptography, Programming Languages
	\end{rSubsection}
	\begin{rSubsection}{B.S. Computer Science}{Fall 2017 -- Spring 2021}{Georgia Institute of Technology}{}
	Concentrations in Intelligence and Media. Major GPA: 4.00, Cumulative GPA: 3.96 \\
	Selected coursework: Automata \& Complexity, Machine Learning, Computer Vision
	\end{rSubsection}
\end{rSection}

\begin{rSection}{Professional Experience}
	\begin{rSubsection}{Georgia Institute of Technology College of Computing}{Fall 2019 -- Fall 2022}{Teaching Assistant, CS 3451: Introduction to Computer Graphics. }{}
		Held help sessions/office hours twice a week, debugged and graded programming homework. Course was taught using TypeScript, WebGL, and Processing. Worked with Greg Turk, Blair MacIntyre, and Jarek Rossignac.
	\end{rSubsection}
	\begin{rSubsection}{Decatur Makers}{Summer 2021}{Digital Infrastructure Intern}{}
		Developed an RFID authentication system to allow members access to the makerspace. Automated time-consuming steps in the process for signing up new members, such as performing background checks.
	\end{rSubsection}
	\begin{rSubsection}{Red Hat, Inc.}{Summer 2019}{Software Engineering Internship}{}
		Added a new feature to Composer (a.k.a. Red Hat Image Builder) to enable automated uploads of RHEL images to cloud providers including AWS, Microsoft Azure, and Google Cloud.
	\end{rSubsection}
	\begin{rSubsection}{Axio Global}{Summer 2018}{Development Intern}{}
		Launched a web platform to facilitate communication between clients and in-house analysts, created tools for visualizing insurance policy coverage, gathered experience building web applications in a fast-paced startup environment.
	\end{rSubsection}
	\begin{rSubsection}{Georgia Institute of Technology School of Mathematics}{Summer 2016, Summer 2017}{Student Assistant}{}
		Developed in-house infrastructure for managing RHEL and macOS systems, monitoring building power usage and coolant flow, and syncing user permissions across services.
	\end{rSubsection}
\end{rSection}

\end{document}
